Algomusicology, ????, Profit

### 2016-04-17 paper.tex
Incorporate some of @namin's feedback.
Incorporate @nadamin's footnote protip.

Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
than we'd like. \footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
Can algomusicology influence music?\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
which is a portmanteau of algorave and musicology, has a self-evident definition.}

@@

Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
takes very little space at all. That's roughly the size all music ever recorded,
described in less than a half a tweet\footnote{Based on the iTunes library featuring approximately 50 million songs
of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
restricted to 140 characters.}.

@@

If we enumerate the Kleene star of a particular alphabet, we get a sequence of all its possible strings.
If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
A lexicon has the property that every finite string is a substring.

@@

As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.\footnote{The encoding scheme is chosen
to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the accompanying code.}

@@

Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
a universal piece of music, any work published subsequent to it infringes on its copyright.\footnote{I am not a lawyer. Do not rely on my legal advice.} In order to convert our algomusicological understanding into profit, we simply have to sue the composers
of every marginally successful musical work from now until they fix the law.

>>>>

Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
which is a portmanteau of algorave and musicology, has a self-evident definition.}

@@

Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
takes very little space at all. That's roughly the size all music ever recorded,
described in less than a half a tweet.~\footnote{Based on the iTunes library featuring approximately 50 million songs
of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
restricted to 140 characters.}

@@

If we enumerate the Kleene star of a particular alphabet, we get a sequence of all its possible strings.
If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
A lexicon contains every finite string as a substring.

@@

As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.~\footnote{The encoding scheme is chosen
to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the accompanying code.}

@@

Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer. Do not rely on my legal advice.} In order to convert our algomusicological understanding into profit, we simply have to sue the composers
of every marginally successful musical work from now until they fix the law.
